\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.2cm, top=1.7cm, right=1.2cm, bottom=1.7cm}

\begin{document}

%----------HEADING-----------------
\begin{center}
    {\LARGE \textbf{Dela Akpalu}}\\
    Newark, NJ | \href{mailto:dela.eak@gmail.com}{dela.eak@gmail.com} | +336-978-6189 | \href{https://linkedin.com/in/edakpalu}{LinkedIn}
\end{center}

\section*{Objective}
\hrule \vspace{3mm}
Dedicated and passionate educator with a strong foundation in mathematics, statistics, and data analysis. Committed to fostering intellectual curiosity and academic excellence through inclusive, student-centered instruction. Experienced in mentoring diverse learners and integrating technology into problem-based learning. Eager to contribute to mathematics and statistics program that emphasizes rigor, real-world relevance, and prepares students for success in higher education and lifelong learning


\section*{Teaching Experience}
\hrule \vspace{2mm}
\textbf{Wake Forest University} -- Teaching Assistant (August 2023 -- May 2025)
\begin{itemize}
    \item Assisted students in data analysis, statistics, and visualization, providing hands-on guidance using R and Python.
    \item Conducted tutoring sessions and study groups to reinforce statistical concepts and analytical methods.
    \item Graded assignments and provided constructive feedback to support student learning and development.
\end{itemize}

\textbf{Kwame Nkrumah University of Science and Technology} -- Teaching Assistant (2020 -- 2022)
\begin{itemize}
    \item Led undergraduate classes in experimental design, algebra, calculus, and statistical methods, using a student-centered, discussion-based approach.
    \item Developed and delivered engaging lessons that made abstract math concepts accessible and relevant.
    \item Mentored students in academic research and data projects, emphasizing collaborative problem-solving and critical thinking.
\end{itemize}

\section*{Skills}
\hrule \vspace{2mm}
\textbf{Teaching and Mentorship}
\begin{itemize}
    \item Designed engaging lesson plans using real-world examples to simplify complex mathematical concepts.
    \item Fostered curiosity through interactive teaching methods, including visual aids and hands-on activities.
    \item Provided individualized support to students, improving comprehension and engagement.
    \item Comfortable transitioning to a high school setting and applying university-level teaching experience to younger learners.
\end{itemize}

\textbf{Integration of Technology in Education}
\begin{itemize}
    \item Utilized tools like Google Classroom and Kahoot! to create interactive assignments and quizzes.
    \item Incorporated multimedia presentations and data visualization techniques to illustrate abstract concepts.
    \item Led technology-driven workshops, teaching students to use statistical software for data analysis.
\end{itemize}

\textbf{Mathematical and Statistical Expertise}
\begin{itemize}
    \item Developed project-based learning activities where students analyzed real-world datasets to understand key statistical concepts.
    \item Simplified advanced topics in probability and regression analysis using practical, relatable examples.
    \item Designed interactive exercises, such as hands-on probability experiments, to engage students in statistical learning.
\end{itemize}

\section*{Education}
\hrule \vspace{2mm}
\textbf{Wake Forest University} -- M.S. in Statistical Science (August 2023 -- May 2025)
\begin{itemize}
    \item Relevant Coursework: Statistical Learning, Probability, Data Visualization, Bayesian Statistics
\end{itemize}

\textbf{African Institute for Mathematical Sciences} -- Structured Masters in Data Science (2022 -- 2023)
\begin{itemize}
    \item Thesis: An Improved Model for Nowcasting Stock Markets Using Machine Learning
\end{itemize}

\textbf{Kwame Nkrumah University of Science and Technology} -- B.S. in Statistics (2016 -- 2020)
\begin{itemize}
    \item Thesis: Survival Analysis of Breast Cancer Patients in Ghana: A Comparative Case Study
\end{itemize}

\section*{Awards and Certifications}
\hrule \vspace{2mm}
\begin{itemize}
    \item Distinguished Teaching Assistant Award (2025) -- Department of Statistical Sciences, Wake Forest University
    \item Data Science Certificate -- Department of Computer Science, Wake Forest University
\end{itemize}
\end{document}
